Seminarium TI 3700\\ Data Analysis on Twitter: An Overview

### 2014-03-26 paper_final.tex
usecase migratie

\subsubsection*{Usecase: Predicting Political Preferences}

%TODO: Add to new chapter

During election time it can be useful to predict the political preferences of a user. In Makazhanov \& Raﬁei's paper a solution to this problem is presented. As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets. \cite{pol} To achieve this (political) hashtags in combination with Twitter activities is used. To know if a user mentions an account of an election candidate a number of these accounts are scraped semi-automaticall. This resulted in the collection of 181972 tweets about politics.\cite{pol}

Before processing these tweets non-personal and spam accounts had to be filtered. Using multiple techniques spam was filtered, but after filtering only 0.3\% of the accounts were labeled as spam. After a manual check none of these accounts seemed to be a spammer. But after removing spam accounts there are still some Non-Personal(NP)-accounts(e.g Businesses, official entities and News Papers)  that should be removed before processing the data. This is mostly done by using the provided profile information and filtering on city names in the user names.  \cite{pol}

After all the preprocessing a one vs all classifier is trained to classify the users. This classifier will recognize one political party vs all other political parties. The classifier will give a confidence score how likely the user will belong to a party. Then all these scores are compared and the user will probably prefer the party with the highest score.  \cite{pol}
\subsection{Tag Based Analysis}

@@

The Linear-Weighted Hybrid model uses the tags as recommendation components whose output is a weighted sum of components $\kappa_1$ through $\kappa_k$. 
Each component $\kappa_i$ has its own value between 0 and 1 computed by the function $\phi_i (u,q,r)$, and a corresponding weight $\alpha_i$, also between
0 and 1. The sum of all weights $\alpha_i$ has to be 1.

Therefore, the hybrid model is defined as the function $\varphi (u, q, r) = \sum\limits_{i = 1}^k \alpha_i \phi_i (u,q,r)$

All weights $\alpha_i$ are then computed by applying a random-restart hill climbing technique. A subset is used as a holdout set, and a vector gets created with random weights that sum to 1. The recommender then modifies the vector over the holdout set to train the algorithm until it reaches a stable point. The algorithm then restarts to avoid local minima.

@@

The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has been developed for the purpose of tag-based recommendation systems. The model can be adapted to compute recommendations from tags used by Twitter. The adaptation involves changing the roles of resources and tags with respect to each other.

This model is restricted in a way because its output is a set of matrices that illustrates a special case of the Tucker decomposition of a tensor. The tensor is not directly linked to the dataset, but rather implies a ranking. It is therefore only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.

To build the model, the data has to be observed in the form $(u, r+, r-, t)$ where $(u, r+, t)$ and $(u, r-, t)$ is a triple respectively
found and not found in the dataset. A ranking function is then used to prefer positive examples over negative ones. An iterative gradient-descent
algorithm is used to optimize this function. All four matrices will be updated until they converge. The matrices represent the factor-reduced components
of the specialised tensor factorization:

$M = U_k R_k^U + T_k R_k^T$

Where 
\begin{itemize}
 \item $U_k$ the user factorization
 \item $T_k$ is the tag factor matrix
 \item $R_k^U$ is the resource factor matrix with respect to the users
 \item $R_k^T$ is the resource factor matrix with respect to the tags
 \item $k$ selected number of factors
 \item $M$ the personalized resource-ranking tensor
\end{itemize}

The relevance score of a resource can now be calculated by:

$\phi (u, \{t\}, r) = \sum_{i=1}^k U_k[u][i]R_k^U[r][i] + T_k[t][i]R_k^T[r][i]$

@@

Then a labelling function is used to label the event, two types of labelling functions are tested. (1) Proximity-based Clustering (PbC) (2) Naive Bayes. PbC is an algorithm similar to K-means with k already known. The collection of tweets $X$ is observed and the class is returned for which the distance of between an event it's mean and the tweet vector is minimized. The Naive Bayes approach uses the formula $y = \arg\max_{y \in Y} P(y)\prod_i P(x_i, y)$ to assign the most probable class label $y \in Y$ to tweet $x$. The Naive Bayes approach outperforms PbC for all feature sets.  \cite{eventalign}
\subsubsection*{Usecase: Earthquake Detection}

%TODO: Add to new chapter

In Sakaki et al. their paper a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} They consider Twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.

To distinguish between tweets about Earthquakes a number of features is used. (1) The number of words in a tweet (2) The words in a tweet (3) Word context features. Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users. With the above feature set as basis, a system that detects earthquakes using Twitter was built. After the system detects an earthquake an email to all users is sent. The system was used during 18. august - 2 September. In this time period 10 earthquakes had occurred, all of these earthquakes were detected. Furthermore Sakaki et al. their system detects an earthquake 10 minutes after happening and sends a message within a minute after detection. 
\cite{earthq}

@@

>>>>

\subsection{Tag Based Analysis}

@@

The Linear-Weighted Hybrid model uses the tags as recommendation components whose output is a weighted sum of components $\kappa_1$ through $\kappa_k$. 
Each component $\kappa_i$ has its own value between 0 and 1 computed by the function $\phi_i (u,q,r)$, and a corresponding weight $\alpha_i$, also between
0 and 1. The sum of all weights $\alpha_i$ has to be 1.
Therefore, the hybrid model is defined as the function $\varphi (u, q, r) = \sum\limits_{i = 1}^k \alpha_i \phi_i (u,q,r)$
All weights $\alpha_i$ are then computed by applying a random-restart hill climbing technique. A subset is used as a holdout set, and a vector gets created with random weights that sum to 1. The recommender then modifies the vector over the holdout set to train the algorithm until it reaches a stable point. The algorithm then restarts to avoid local minima.

@@

The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has been developed for the purpose of tag-based recommendation systems. The model can be adapted to compute recommendations from tags used by Twitter. The adaptation involves changing the roles of resources and tags with respect to each other.
This model is restricted in a way because its output is a set of matrices that illustrates a special case of the Tucker decomposition of a tensor. The tensor is not directly linked to the dataset, but rather implies a ranking. It is therefore only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.
To build the model, the data has to be observed in the form $(u, r+, r-, t)$ where $(u, r+, t)$ and $(u, r-, t)$ is a triple respectively
found and not found in the dataset. A ranking function is then used to prefer positive examples over negative ones. An iterative gradient-descent
algorithm is used to optimize this function. All four matrices will be updated until they converge. The matrices represent the factor-reduced components
of the specialised tensor factorization:
$M = U_k R_k^U + T_k R_k^T$
Where 
\begin{itemize}
 \item $U_k$ the user factorization
 \item $T_k$ is the tag factor matrix
 \item $R_k^U$ is the resource factor matrix with respect to the users
 \item $R_k^T$ is the resource factor matrix with respect to the tags
 \item $k$ selected number of factors
 \item $M$ the personalized resource-ranking tensor
\end{itemize}
The relevance score of a resource can now be calculated by:
$\phi (u, \{t\}, r) = \sum_{i=1}^k U_k[u][i]R_k^U[r][i] + T_k[t][i]R_k^T[r][i]$

@@

Then a labelling function is used to label the event, two types of labelling functions are tested. (1) Proximity-based Clustering (PbC) (2) Naive Bayes. PbC is an algorithm similar to K-means with k already known. The collection of tweets $X$ is observed and the class is returned for which the distance of between an event it's mean and the tweet vector is minimized. The Naive Bayes approach uses the formula $y = \arg\max_{y \in Y} P(y)\prod_i P(x_i, y)$ to assign the most probable class label $y \in Y$ to tweet $x$. The Naive Bayes approach outperforms PbC for all feature sets.  \cite{eventalign}

@@

\subsection*{Predicting Political Preferences using User Classification}

During election time it can be useful to predict the political preferences of a user. In Makazhanov \& Raﬁei's paper a solution to this problem is presented. 
As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets. \cite{pol} To achieve this 
(political) hashtags in combination with Twitter activities is used. To know if a user mentions an account of an election candidate a number of these 
accounts are scraped semi-automaticall. This resulted in the collection of 181972 tweets about politics.\cite{pol}
Before processing these tweets non-personal and spam accounts had to be filtered. Using multiple techniques spam was filtered, but after filtering 
only 0.3\% of the accounts were labeled as spam. After a manual check none of these accounts seemed to be a spammer. But after removing spam accounts 
there are still some Non-Personal(NP)-accounts(e.g Businesses, official entities and News Papers)  that should be removed before processing the data. 
This is mostly done by using the provided profile information and filtering on city names in the user names.  \cite{pol}
After all the preprocessing a one vs all classifier is trained to classify the users. This classifier will recognize one political party vs all other 
political parties. The classifier will give a confidence score how likely the user will belong to a party. Then all these scores are compared and the user 
will probably prefer the party with the highest score.  \cite{pol}

\subsection*{Earthquake Detection using Event Detection}

In Sakaki et al. their paper a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} They consider 
Twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an 
earthquake is occurring. 
To distinguish between tweets about Earthquakes a number of features is used. (1) The number of words in a tweet (2) The words in a tweet (3) Word context 
features. Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users. With the above 
feature set as basis, a system that detects earthquakes using Twitter was built. After the system detects an earthquake an email to all users is sent. 
The system was used during 18. august - 2 September. In this time period 10 earthquakes had occurred, all of these earthquakes were detected. Furthermore 
Sakaki et al. their system detects an earthquake 10 minutes after happening and sends a message within a minute after detection. 
\cite{earthq}
